% !TEX program = pdflatex
% !TEX root = resume.tex
\documentclass[11pt, a4paper]{article}

% Packages
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Colors (Awesome CV style usually uses a dark red/accent color)
\definecolor{awesome-red}{HTML}{DC3522}
\definecolor{darkgray}{HTML}{333333}
\definecolor{gray}{HTML}{5D5D5D}

% Links setup
\hypersetup{
    colorlinks=true,
    linkcolor=awesome-red,
    filecolor=awesome-red,      
    urlcolor=awesome-red,
}

% Fonts (Default LaTeX font is fine, or use helvet/arial if preferred)
% \usepackage[default]{lato} % Requires lato package

% Section Formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{awesome-red}
}{}{0em}{}[\color{darkgray}\titlerule \vspace{-5pt}]

% Subsection Formatting
\titleformat{\subsection}{
  \vspace{-2pt}\raggedright\large\bfseries\color{darkgray}
}{}{0em}{}

% Custom commands for the resume
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{XINGYUAN ZHAO}} \\ \vspace{5pt}
    \small McKinney, TX 75070, US $|$ \small +1 (806) 800 6806 $|$ \href{mailto:xingyuanzhao@pm.me}{xingyuanzhao@pm.me} $|$ \href{https://github.com/YOUR-GITHUB}{github.com/YOUR-GITHUB}
\end{center}

% Summary
\section{Summary}
\small Technical builder with hands-on experience in LLM fine-tuning, AI agent development, and GPU-accelerated ML pipelines. Independently designed and implemented novel algorithms integrating transformer attention mechanisms into causal inference methods. Built end-to-end NLP systems for event extraction and argument linking from large-scale unstructured text. Strong mathematical foundation in linear algebra, probability, and statistical inference. Fast learner who bridges cutting-edge ML research with practical implementation.

% Skills
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical}{: LLM Integration \& Fine-tuning, AI Agent Architecture, Machine Learning, Natural Language Processing, GPU-accelerated computations} \\
     \textbf{Data Analysis}{: Statistical Analysis \& Experiment design, Causal Inference, Database Structures} \\
     \textbf{Mathematics}{: Linear Algebra, Probability Theory, Statistical Inference, Optimization} \\
     \textbf{Programming}{: Python (PyTorch, TensorFlow, HuggingFace Transformers, scikit-learn, pandas), R, SQL, Git}
    }}
\end{itemize}

% Experience
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {University of Texas at Dallas}{Richardson, Texas, US}
      {Lecturer}{05/2024 -- Current}
      \resumeItemListStart
        \resumeItem{Taught the following classes: Data Visualization, Methods of Data Collection and Production, Knowledge Mining, Introduction to Quantitative Methods, and State and Local Government.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Texas at Dallas}{Richardson, Texas, US}
      {Research Assistant}{05/2024 -- Current}
      \resumeItemListStart
        \resumeItem{Built custom attention-based synthetic control algorithm from scratch using PyTorch.}
        \resumeItem{Fine-tuned BERT and transformer models for political text classification on GPU cluster.}
        \resumeItem{Developed AI agent pipeline for event extraction from large-scale unstructured text data.}
        \resumeItem{Implemented end-to-end NLP system processing 500K+ social media posts using HuggingFace Transformers.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Texas at Dallas}{Richardson, Texas, US}
      {Teaching Assistant}{08/2022 -- Current}
      \resumeItemListStart
        \resumeItem{Conducted workshops on data analysis for the Transfer Research Initiative.}
        \resumeItem{Led coding sessions at the Math and Coding Camp.}
      \resumeItemListEnd

    \resumeSubheading
      {Beijing Bytedance Technology Co. Ltd.}{Haidian, Beijing, China}
      {Public Affairs Specialist}{}
      \resumeItemListStart
        \resumeItem{Analyzing local policy trends and related data.}
        \resumeItem{Maintaining relationships with agencies.}
        \resumeItem{Leading and managing a group of interns.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

% Education
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Dallas}{Richardson, TX}
      {Ph.D. in Political Science}{Expected 04/2026}
    
    \resumeSubheading
      {University of Texas at Dallas}{Richardson, TX}
      {Master of Science in Social Data Analytics and Research}{Expected 04/2026}
\resumeSubHeadingListEnd

% Technical Projects
\section{Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{AI Agent for Event Extraction from Unstructured Text} $|$ \emph{Independent Project}}{}
      \resumeItemListStart
        \resumeItem{Independently built an AI agent system to extract structured events from messy, unstructured text data.}
        \resumeItem{Designed multi-step reasoning pipeline with LLM orchestration for robust information extraction.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Event Argument Extraction \& Multi-Sentence Argument Linking} $|$ \emph{Independent Project}}{}
      \resumeItemListStart
        \resumeItem{Independently developed NLP system for extracting event arguments and linking arguments across multiple sentences.}
        \resumeItem{Implemented transformer-based architecture for cross-sentence semantic reasoning.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Attention-Based Synthetic Control Method} $|$ \emph{MPSA Conference}}{}
      \resumeItemListStart
        \resumeItem{Independently designed and implemented a novel causal inference algorithm integrating multi-head attention mechanism into synthetic control methods using PyTorch.}
        \resumeItem{Built custom attention layers to refine donor unit weighting, improving pretreatment alignment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Large-Scale Political Text Analysis Pipeline} $|$ \emph{MPSA Conference}}{}
      \resumeItemListStart
        \resumeItem{Independently built end-to-end NLP pipeline for analyzing political polarization patterns from 500K+ social media posts.}
        \resumeItem{Implemented BERT-based text classification and topic modeling for stance detection.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{GPU Export Policy Impact Analysis} $|$ \emph{Working in Progress}}{}
      \resumeItemListStart
        \resumeItem{Independently designed empirical framework analyzing BIS GPU regulations' effect on US-China AI development trajectories.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

% Certifications
\section{Certifications}
\resumeSubHeadingListStart
    \resumeItem{Computing in Python IV: Objects \& Algorithms from Georgia Tech GTX}
    \resumeItem{Statistical Learning from Stanford Online}
\resumeSubHeadingListEnd

\end{document}
